# **Overview**
 Since 2008, guests and hosts have used Airbnb to expand on traveling possibilities
 and present more unique, personalized way of experiencing the world.This dataset describes
 the listing activity and metrics in NYC, NY for 2019.

```{r }
# installing packages

# loading libraries
library(ggplot2)
library(e1071)
library(scales)
library(dplyr)
library(tidyr)
library(RColorBrewer)
```

***Importing Datasets***
```{r}
our.data = read.csv("input/AB_NYC_2019.csv", stringsAsFactors = F)
```

***Data Preprocessing***
```{r}
dim(our.data)
```

```{r}
str(our.data)
```

```{r include=FALSE}
get_missing_data_df = function(x){
  column_names = c()
  missing_count = c()
  missing_percent = c()
  
  for (i in 1:ncol(x)) {
    if(sum(is.na(x[i])) > 0){
      column_name = names(x[i])
      count = sum(is.na(x[i]))
      per = round((count*100 / nrow(x)), 2)
      
      column_names = c(column_names, column_name)
      missing_count = c(missing_count, count)
      missing_percent = c(missing_percent, per)
    }
  }
  
  missing_df = data.frame(column_name = column_names, missing_count = missing_count, 
                          missing_percent = missing_percent)
  
  return(missing_df)
}

```


*Missing Values*
```{r}
# user defined function to find the columns having missing values
missing_df = get_missing_data_df(our.data) 
missing_df
```

*Note*: only 'reviews_per_month' variable has missing values we'll replace all NA's with 0.

```{r}
our.data$reviews_per_month = ifelse(is.na(our.data$reviews_per_month), 0, 
                                    our.data$reviews_per_month)
```

*Note*: Still it might be possible that some variables contains empty fields, which we'll handle in our exploratory analysis.

***Exploratory Analysis***
```{r}
# Dropping 'Id' and 'host_name' from our dataset as they are insignificant.
our.data = our.data[, -c(1, 4)]
head(our.data, 4)
```

Exploring Columns

* Price
```{r}
# Price - Plot Density Graph

ggplot(data = our.data, mapping = aes(x = price)) +
  geom_density(fill = "#45d16a", col = "#054516", alpha = 0.8) +
  ggtitle("Price Density Graph")
```

```{r}
skewness(our.data$price)
```

*NOTE:* We observe that price is highly right skewed, that means a large amount of property price is less than $500.

* Minimum Nights
```{r}
length(unique(our.data$minimum_nights))
```

```{r}
# Scatter plot between Price and minimum_nights
ggplot(data = our.data, mapping = aes(x = minimum_nights, y = price)) +
  geom_point(col = '#7ef79e') +
  ggtitle("Price Vs Minimum_Nights") +
  ylab("Price") +
  xlab("Minimum Nights")
```

* Neighbourhood_group
```{r}
length(unique(our.data$neighbourhood_group))
unique(our.data$neighbourhood_group)
```

This variable is seems to be a categorical variable, hence changing this variable to factors.


```{r}
# Neighbourhood_group and price
our.data$neighbourhood_group = as.factor(our.data$neighbourhood_group)

```

Creating a new data frame which contains the price median value for each neighbourhood group.
```{r}
price_per_neighbourhood_group = our.data %>% 
  group_by(neighbourhood_group) %>%
  summarise(median_price = median(price))

price_per_neighbourhood_group
```

A bar graph for Neighbourhood group based on their property price.
```{r}
ggplot(data = price_per_neighbourhood_group, mapping = aes(x = reorder(neighbourhood_group, median_price), 
                                                           y = median_price)) + 
  geom_bar(stat = 'identity', fill = '#5188e0', col = '#095ee6', alpha = 0.8) +
  coord_flip() +
  ggtitle("Median price per neighbourhood group") +
  xlab("Neighbourhood group") +
  ylab("Median Price") +
  scale_y_continuous(labels = dollar) +
  geom_label(mapping = aes(label = paste('$', median_price)))
```

*NOTE:* Property price at Manhattan is highest among them and Bronx has the lowest.

* Room Type
```{r}
unique(our.data$room_type)
```

This variable is seems to be a categorical variable, hence changing it to factors.
```{r}
our.data$room_type = as.factor(our.data$room_type)
```

Plot a bar graph for room type
```{r}
ggplot(data = our.data, mapping = aes(x = room_type)) +
  geom_bar(fill = '#66edd4', col = '#07876f', alpha = 0.8) +
  ggtitle("Room Type Analysis") +
  xlab("Room Type") +
  ylab("Count") +
  geom_label(mapping = aes(label = ..count..), stat = 'count')

```

*NOTE:* Number of 'Entire home/apt' and 'Private room' is much larger than that of shared room in our data set.

Creating a new data frame which contains the price median value for each room type.
```{r}
room_type_price_df = our.data %>%
  group_by(room_type) %>%
  summarise(median_price = median(price))

room_type_price_df
```

Plot a bar graph for Room type and their Price (Median)

```{r}
ggplot(data = room_type_price_df, mapping = aes(x = reorder(room_type, median_price), y = median_price)) +
  geom_bar(stat = 'identity', fill='#8eba47', col='#2a4006', alpha = 0.8) +
  coord_flip() +
  ggtitle("Room Type and their price (median)") +
  xlab("Room Type") +
  ylab("Median Price") +
  scale_y_continuous(labels = dollar) + 
  geom_label(mapping = aes(label = paste("$", median_price)))
```

*NOTE:* Price of 'Entire home/apt' is higher than that of 'Private Room' or 'Shared room'.

Creating a dataframe that contains the percentage of room_type present in particular neighbourhood_group.

```{r}

neigh_room.df = our.data %>%
  group_by(neighbourhood_group, room_type) %>%
  summarise(count_room = n())

neigh_count = neigh_room.df %>%
  group_by(neighbourhood_group) %>%
  summarise(sum = sum(count_room))

percent_vec = c()

percent_vec = ifelse(neigh_room.df$neighbourhood_group == 'Bronx', 
                     neigh_room.df$count_room/neigh_count$sum[1], 0)
percent_vec = ifelse(neigh_room.df$neighbourhood_group == 'Brooklyn', 
                     neigh_room.df$count_room/neigh_count$sum[2], percent_vec)
percent_vec = ifelse(neigh_room.df$neighbourhood_group == 'Manhattan', 
                     neigh_room.df$count_room/neigh_count$sum[3], percent_vec)
percent_vec = ifelse(neigh_room.df$neighbourhood_group == 'Queens', 
                     neigh_room.df$count_room/neigh_count$sum[4], percent_vec)
percent_vec = ifelse(neigh_room.df$neighbourhood_group == 'Staten Island', 
                     neigh_room.df$count_room/neigh_count$sum[5], percent_vec)

neigh_room.df$percentage = round(percent_vec*100, 2)

neigh_room.df
```

Plotting bar graphs to find the relationship between Neighbourhood Group and Room Type.

```{r out.width='150%'}
ggplot(neigh_room.df, aes(room_type, percentage)) + 
  geom_bar(stat = 'identity', fill='#f5ae62', col='#8a4f0f', alpha = 0.8, width = 0.5) + 
  facet_grid(~ neighbourhood_group) +
  geom_label(mapping = aes(label = paste(percentage, "%"))) +
  ggtitle("Percentage of room type per neighbourhood area") +
  xlab("Percentage") +
  ylab("Room Type") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, vjust = 1))
```

*NOTE:* From RoomType percentage Neighbourhood area, we found out that:

* **Manhattan** - large number of *Entire home* peresent as compared to *Private* and *shared*.
* Similary, **Bronx** and **Queens** - More number of *Private room* present as compared to *Entire home* and *shared*.
* **Broooklyn** and **Staten Island** - Have almost same number of *Entire* or *Private* property available.